### 2018-07-25 doc/plos/text/manuscript.tex
MASE rewording

Because wILI is subject to revision over multiple months, a real-time naive
nowcast would be defined as \textit{preliminary} wILI on the preceding week.
However, preliminary versions of wILI are not generally known today (except for
within a narrow set of locations and seasons). As a result, we introduce the
``Naive Oracle'' nowcaster. This assumes (incorrectly) that the final version
of wILI is known with no delay and defines the naive nowcast as \textit{final}
wILI on the preceding week. Since this information is not available at runtime,
the Naive Oracle is unfairly advantaged. As such, MASE is reasonably subject to
being greater than one, indicating that the nowcast under consideration
performed \textit{worse} than the ``naive'' nowcast. This should be
unsurprising, if not expected, given that the Naive Oracle incorporates
information which is not available at runtime. In any case, MASE is a useful
measure for comparing the performance of a given nowcast across different
locations.

Given the above discussion of the Naive Oracle, we define the naive nowcast for
any given location on any given week as the final value of ground truth in the
same location one week earlier. Using the same notation as above, and
considering the $m$ weeks for which ground truth is available on the prior
week, MASE is defined as:

>>>>

Because wILI is subject to revision over multiple months, a real-time naive
nowcast would be defined as \textit{preliminary} wILI on the preceding week.
However, preliminary versions of wILI are not generally known today (except for
within a narrow set of locations and seasons). As a result, we introduce the
``Naive Oracle'' nowcaster. This assumes (incorrectly) that the final version
of wILI is known with no delay and defines the naive nowcast as \textit{final}
wILI on the preceding week. Since this information is not available at runtime,
the Naive Oracle is unfairly advantaged. As such, MASE is reasonably subject to
being greater than one, indicating that the nowcast under consideration
performed \textit{worse} than the ``naive'' nowcast. This should be
unsurprising, if not expected, given that the Naive Oracle incorporates
information which is not available at runtime. In any case, while MASE is not
particularly helpful as an absolute measure of accuracy, MASE is useful for
comparing relative accuracy between different locations.

We define the naive nowcast for any given location on any given week as the
final value of ground truth in the same location one week earlier. Using the
same notation as above, and considering the $m$ weeks for which ground truth is
available on the prior week, MASE is defined as:
